Interoception Scale (Study 2) - Data Cleaning

### 2025-12-29 paper/manuscript.qmd
added omega for ERS and CERQ

The Emotion Reactivity Scale - Brief Version [B-ERS, @veilleux2024development] measures 3 dimensions with 6 items on a 5-point Likert scale (0 = *Not like me at all*, 4 = *Extremely like me*): Arousal (*"My moods are very strong and powerful"*), Sensitivity (*"I tend to get very emotional very easily"*), and Persistence (*"When I am angry/upset, it takes me much longer than most people to calm down"*).

The Cognitive Emotion Regulation Questionnaire [CERQ-short, @garnefski2006cognitive] measures 9 adaptive and maladaptive emotion regulation strategies with 18 items (1 = *Almost Never*, 5 = *Almost Always*). The strategies include Self-blame, Other-blame, Rumination, Catastrophizing, Putting into Perspective, Positive Refocusing, Positive Reappraisal, Acceptance, and Planning.

>>>>

The Emotion Reactivity Scale - Brief Version [B-ERS, @veilleux2024development] measures 3 dimensions with 6 items on a 5-point Likert scale (0 = *Not like me at all*, 4 = *Extremely like me*): Arousal (*"My moods are very strong and powerful"*), Sensitivity (*"I tend to get very emotional very easily"*), and Persistence (*"When I am angry/upset, it takes me much longer than most people to calm down"*). The subscales of the B-ERS showed acceptable to good internal consistency: ωArousal = 0.76, ωSensitivity = 0.90 and ωPersistence = 0.74.

The Cognitive Emotion Regulation Questionnaire [CERQ-short, @garnefski2006cognitive] measures 9 adaptive and maladaptive emotion regulation strategies with 18 items (1 = *Almost Never*, 5 = *Almost Always*). The strategies include Self-blame (ω= 0.78), Other-blame (ω= 0.8), Rumination (ω= 0.61), Catastrophizing (ω= 0.84), Putting into Perspective (ω= 0.70), Positive Refocusing (ω= 0.80), Positive Reappraisal (ω= 0.75), Acceptance (ω= 0.75), and Planning (ω= 0.66). The internal consistency for these dimensions ranged from acceptable to good.

### 2025-12-29 study2/analysis/1_cleaning.qmd
added omega for ERS and CERQ

>>>>

```{r}
ers_a <- df[, grepl("^ERS_Arousal_", names(df))]
ers_s <-  df[, grepl("^ERS_Sensitivity_", names(df))]
ers_p <-  df[, grepl("^ERS_Persistence_", names(df))]

psych::omega(ers_a, nfactors = 1)
psych::omega(tas_ddf, nfactors = 1)
psych::omega(tas_dif, nfactors = 1)

```{r}
cerq_acept <- df[, grepl("^CERQ_Acceptance_", names(df))]
cerq_posref <- df[, grepl("^CERQ_PositiveRefocusing_", names(df))]
cerq_posrea <- df[, grepl("^CERQ_PositiveReappraisal_", names(df))]
cerq_selfbla <- df[, grepl("^CERQ_SelfBlame_", names(df))]
cerq_otherbla <- df[, grepl("^CERQ_OtherBlame_", names(df))]
cerq_rum <- df[, grepl("^CERQ_Rumination_", names(df))]
cerq_cat <- df[, grepl("^CERQ_Catastrophizing_", names(df))]
cerq_refopla <- df[, grepl("^CERQ_RefocusPlanning_", names(df))]
cerq_persp <- df[, grepl("^CERQ_Perspective_", names(df))]

psych::omega(cerq_acept, nfactors = 1)
psych::omega(cerq_posref, nfactors = 1)
psych::omega(cerq_posrea, nfactors = 1)
psych::omega(cerq_selfbla, nfactors = 1)
psych::omega(cerq_otherbla, nfactors = 1)
psych::omega(cerq_rum, nfactors = 1)
psych::omega(cerq_cat, nfactors = 1)
psych::omega(cerq_refopla, nfactors = 1)
psych::omega(cerq_persp, nfactors = 1)
```
